### 2013-12-16 Paper_Markdown.Rmd
Re-ran the markdown file & updating wapls.res.RData
Re-compiled the markdown file but noticed an error with the wapls.res
files.  I've fixed that up (hence edits to bootstrap_wapls.R)  and have
a partially complete wapls.res file as well.  Approx 60% done.  It seems
a lot slower than usual though.
Removed free scales for the plotting (except this screws up wapls plots!), e-ran wa.res to try to fix bug.  Partial run results (up to 16 runs).

```{r LoadData, echo=FALSE, warning=FALSE, message=FALSE}
library(gridExtra)

@@

ggplot(model.samp, aes(x = dissim, y = preds, group = site, color = init)) +
  geom_path(alpha = 0.1) +
  theme_bw() +
  facet_wrap(~model, scales='free_y', nrow = 1) +
  scale_x_continuous(expand=c(0,0)) +
  scale_color_continuous(low='#F08080', high='#4169E1') +
  theme(legend.position = 'top',
        axis.title = element_text(family = 'serif', face = 'bold', size = 14),
        strip.text = element_text(family = 'serif', face = 'bold', size = 14),
        axis.text = element_text(family = 'serif', size = 10),
        strip.text = element_text(family = 'serif', face = 'bold', size = 12)) +
  xlab('Calibration Dissimilarity') +
  ylab('Predicted Value')

>>>>

```{r LoadData, echo=FALSE, warning=FALSE, message=FALSE}

@@

ggplot(model.samp, aes(x = dissim, y = preds, group = site, color = init)) +
  geom_path(alpha = 0.1) +
  theme_bw() +
  facet_wrap(~model, nrow = 1) +
  scale_x_continuous(expand=c(0,0)) +
  scale_color_continuous(low='#F08080', high='#4169E1') +
  theme(legend.position = 'top',
        axis.title = element_text(family = 'serif', face = 'bold', size = 14),
        strip.text = element_text(family = 'serif', face = 'bold', size = 14),
        axis.text = element_text(family = 'serif', size = 10),
        strip.text = element_text(family = 'serif', face = 'bold', size = 12)) +
  xlab('Calibration Dissimilarity') +
  ylab('Predicted Value')
